PM Mungbean meta-analysis

### 2019-06-20 03_Preliminary_analysis.Rmd
remove old analysis

```{r PA_Libraries}
library(dplyr)
library(openxlsx)
library(kableExtra)
library(ggplot2)
library(devtools)
#source("./getPPD2.R")

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, include= FALSE}
library(lme4)

# Which row spacing leads to the highest yield penalty

# `2017-05-11` # last assessment Fogerty
subset(PM_MB_17, location == "Hermitage")
ggplot(subset(PM_MB_17, Treatment.No == "T1"||"1"), 
       aes(y = Incidence, x = Incidence_assessment_date, colour = location))+
   geom_point()+
   geom_smooth()+
   scale_y_continuous(limits = c(-5,15))
# PM_MB_means <- subset(PM_MB_means, Fungicide != "control")   
# PM_MB_means$Fungicide <- factor(PM_MB_means$Fungicide, levels = c("Sulphur", "Amistar", "propiconazole", "Tebeconazole"))
PM_MB_means$Fungicide <- factor(PM_MB_means$Fungicide, levels = c("control", "Sulphur", "Amistar", "propiconazole", "Tebeconazole"))
yield_lmer1 <- lmer(`yield_gain` ~ factor(total_Fungicide) + Fungicide + factor(Year) + (factor(Year)|Location), 
                    data = PM_MB_means, na.action = na.omit, REML = F)
# removed the Year interaction with location
yield_lmer2 <- lmer(`yield_gain` ~ factor(total_Fungicide) + Fungicide + factor(Year) + (1|Location), 
                    data = PM_MB_means, na.action = na.omit, REML = F)
# Removing Fungicide as different fungicides were sprayed a different number of times
yield_lmer3 <- lmer(`yield_gain` ~ factor(total_Fungicide)  + factor(Year) + (1|Location), 
                    data = PM_MB_means, na.action = na.omit, REML = F)
# Removing Fungicide as different fungicides were sprayed a different number of times
yield_lmer4 <- lmer(`yield_gain` ~ factor(total_Fungicide)  + factor(Year) + (1|Location) + (1|Fungicide), 
                    data = PM_MB_means, na.action = na.omit, REML = T)
ranef(yield_lmer4)
anova(yield_lmer1, yield_lmer2) # P = 0.8943  # removed random intercept 'Year' for each random slope 'Location' # Keep simpler model 
anova(yield_lmer2, yield_lmer3) # P = 0.8005  # Removed (FE) Fungicide     #     Fungicide showed not to be significant in protecting yield
anova(yield_lmer3, yield_lmer4) # P = 1       # Added Fungicide as a random effect #     Fungicide showed not to contribute to variation and 
yield_lmer <- lmer(`yield_gain` ~ factor(total_Fungicide) + factor(Year) + (1|Location), 
                    data = PM_MB_means, na.action = na.omit)
summary(yield_lmer)
ranef(yield_lmer)
```

>>>>

```{r PA_Libraries}
library(dplyr)
library(openxlsx)
library(kableExtra)
library(ggplot2)
library(devtools)
library(lme4)
library(theme.usq)
#source("./getPPD2.R")

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, include= FALSE}
# Import data
PM_MB_means <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv")

# Which row spacing leads to the higher disease severity
PM_MB_means %>%
   filter(Year >= 2017)%>%
   filter(Fungicide == "control") %>%
ggplot(aes(y = PM_final_severity, x = row_spacing, colour = Location))+
   geom_point()+
   geom_smooth()+
   scale_y_continuous(limits = c(-5,15))+
   theme_usq()

# Which row spacing leads to the higher yeild potential
PM_MB_means %>%
   filter(Year >= 2017)%>%
#   filter(Fungicide == "control") %>%
ggplot(aes(y = as.numeric(grain_yield.t.ha.), x = row_spacing, colour = Location))+
   geom_jitter(width = 0.01)+
   geom_smooth()+
#   scale_y_continuous(limits = c(-5,15))+
   theme_usq()
